Value Ordering, Discrepancies, and Restarts for Subgraph Algorithms\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/026842/1 and EP/M508056/1]}

### 2018-01-07 paper/paper.tex
Betterer

?? Two recent maximum common induced subgraph algorithms: k${\downarrow}$
\citep{DBLP:conf/aaai/HoffmannMR17}, and McSplit \citep{DBLP:conf/ijcai/McCreeshPT17}. The former
attempts to solve the problem by first trying to solve the induced subgraph isomorphism problem, and
then if that fails, retries allowing a single unmatched vertex (and thus using weaker invariants),
and so on. Due to its similarity to \cref{algorithm:sip}, we can introduce the same bias and restart
strategy.

@@

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-mcsplit.pdf}
    \caption{McSplit speedups ?? partial data, can cut for space and just use
    cumulatives if necessary}\label{figure:mcsplit}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-kdown.pdf}
    \caption{k${\downarrow}$ speedups ?? missing data, can cut for space and just use
    cumulatives if necessary}\label{figure:kdown}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-mcs.pdf}
    \caption{k${\downarrow}$ and McSplit cumulative curves ?? partial and missing
    data}\label{figure:mcs}
\end{figure}

>>>>

?? Two recent maximum common induced subgraph algorithms: k${\downarrow}$
\citep{DBLP:conf/aaai/HoffmannMR17}, and McSplit \citep{DBLP:conf/ijcai/McCreeshPT17}. The former
attempts to solve the problem by first trying to solve the induced subgraph isomorphism problem, and
then if that fails, retries allowing a single unmatched vertex (and thus using weaker invariants),
and so on. Due to its similarity to \cref{algorithm:sip}, we can introduce the same bias and restart
strategy, requiring only a small amount of jiggery-pokery to handle wildcards in nogoods.

@@

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-mcsplit.pdf}
    \caption{McSplit speedups}\label{figure:mcsplit}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-kdown.pdf}
    \caption{k${\downarrow}$ speedups}\label{figure:kdown}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-mcs.pdf}
    \caption{k${\downarrow}$ and McSplit cumulative curves}\label{figure:mcs}
\end{figure}
